Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-04-20 sources/bmc_template_submission/bmc_article.tex
page 1 MK edits

\begin{keyword}
\kwd{gene tree}
\kwd{interoperability}
\kwd{open science}
\kwd{reproducibility}
\kwd{public database}
\kwd{DNA alignment}
\end{keyword}

@@

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Background}
Phylogenies capture the shared history of organisms and provide key evolutionary
context for our biological observations \cite{dobzhansky1973nothing}.
Updating existing phylogenies with publicly available molecular sequence data provides
the opportunity to study
the evolutionary history of many taxa in a reproducible and continuous manner.
Here, we introduce Physcraper, a tool that establishes a data interoperability
framework for biological databases to automate data connections across databases.
Physcraper's main goal is to build upon published alignments to extend existing
phylogenetic inferences with more data and taxa, which improve
phylogenetic reconstruction \cite{hillis1996inferring, natsidis2019phylogenomics},
time of divergence estimates \cite{schulte2013undersampling, soares2015influence},
biogeographic analyses \cite{kayaalp2017back},
as well as help in resolving phylogenetic conflict \cite{hedtke2006resolution, townsend2010optimal, natsidis2019phylogenomics}.
Physcraper updates a starting single locus alignment and corresponding tree
with public DNA data, and links the tips in the updated trees to a unified, interoperable
taxonomic resource \cite{rees2017automated}.

>>>>

\begin{keyword}
\kwd{gene tree}
\kwd{interoperability}
\kwd{open science}
\kwd{reproducibility}
\kwd{public database}
\kwd{DNA alignment}
\kwd{Open Tree of Life}
\kwd{otol}
\end{keyword}

@@

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Background}
Phylogenies capture the shared history of organisms and provide key evolutionary
context for our biological observations \cite{dobzhansky1973nothing}.
Updating existing phylogenies with publicly available molecular sequence data provides
the opportunity to study
the evolutionary history of many taxa in a reproducible and continuous manner.
Here, we introduce Physcraper, a tool that establishes a data interoperability
framework for biological databases to automate data connections across databases.
Physcraper's main goal is to build upon published alignments and published phylogenies
to extend existing phylogenetic inferences with more data and taxa, which improve
phylogenetic reconstruction \cite{hillis1996inferring, natsidis2019phylogenomics},
time of divergence estimates \cite{schulte2013undersampling, soares2015influence},
biogeographic analyses \cite{kayaalp2017back},
as well as help in resolving phylogenetic conflict \cite{hedtke2006resolution, townsend2010optimal, natsidis2019phylogenomics}.
Physcraper updates a starting single locus alignment and corresponding tree
with public DNA data, and links the tips in the updated trees to a unified, interoperable
taxonomic resource \cite{rees2017automated}.
